Spatio-Temporal Modeling and Simulation

### 2024-06-15 report/Report.tex
wip

\subsection{Fitting an Odds Model}

@@

$$\partial_{\phi_{js_ji}}\ln{\mathcal{L}}
=
\frac{1}{P_i'(v_{js_j} | \eta_{js_j})}\frac{\sum_p e^{\phi_{jpi}}-e^{\phi_{js_ji}}}{\left( \sum_p e^{\phi_{jpi}} \right)^2} e^{\phi_{js_ji}}
=
\frac{1}{\sum_p e^{\phi_{jpi}}}\frac{\left(1-P_i'(v_{js_j} | \eta_{js_j}) \right)}{P_i'(v_{js_j} | \eta_{js_j})} e^{\phi_{js_ji}}$$

$$\partial_{\phi_{j\not{s_j}i}}\ln{\mathcal{L}}
=
\frac{1}{P_i'(v_{js_j} | \eta_{js_j})}\frac{-e^{\phi_{js_ji}}}{\left( \sum_p e^{\phi_{jpi}} \right)^2} e^{\phi_{j\not{s_j}i}}
= 
\frac{-1 }{\sum_p e^{\phi_{jpi}}}e^{\phi_{j\not{s_j}i}}$$

@@

$$\partial_Z \ln{\mathcal{L}}=\sum_{\phi_{js_ji} \in Z}\frac{1}{\sum_p \phi_{jpi}}\frac{\left(1-P_i'(v_{js_j} | \eta_{js_j}) \right)}{P_i'(v_{js_j} | \eta_{js_j})}e^{\phi_{js_ji}}-\sum_{\phi_{j\not{s_j}i}\in Z}\frac{1 }{\sum_p \phi_{jpi}}e^{\phi_{j\not{s_j}i}}$$

@@

$$\partial_{\phi_{js_ji}}\ln{\mathcal{L}}=\frac{1}{\sum_p e^{\phi_{jpi}}}\frac{\left(1-P_i'(v_{js_j} | \eta_{js_j}) \right)}{P_i'(v_{js_j} | \eta_{js_j})}e^{\phi_{js_ji}}$$

$$\partial_{\phi_{j\not{s_j}i}}\ln{\mathcal{L}}=\frac{-1 }{\sum_p e^{\phi_{jpi}}}e^{\phi_{j\not{s_j}i}}$$ 
\end{enumerate}

>>>>

\subsection{Fitting a Log Odds Model}

@@

$$\partial_{\phi_{js_ji}}\ln{\mathcal{L}}
=
\frac{1}{P_i'(v_{js_j} | \eta_{js_j})}\frac{\sum_p e^{\phi_{jpi}}-e^{\phi_{js_ji}}}{\left( \sum_p e^{\phi_{jpi}} \right)^2} e^{\phi_{js_ji}}
=
1-P_i'(v_{js_j} | \eta_{js_j})$$

$$\partial_{\phi_{j\not{s_j}i}}\ln{\mathcal{L}}
=
\frac{1}{P_i'(v_{js_j} | \eta_{js_j})}\frac{-e^{\phi_{js_ji}}}{\left( \sum_p e^{\phi_{jpi}} \right)^2} e^{\phi_{j\not{s_j}i}}
= 
-P_i'(v_{j\not{s_j}} | \eta_{j\not{s_j}})$$

@@

$$\partial_Z \ln{\mathcal{L}}=\sum_{\phi_{js_ji} \in Z}\left( 1-P_i'(v_{js_j} | \eta_{js_j}) \right)-\sum_{\phi_{j\not{s_j}i}\in Z}P_i'(v_{j\not{s_j}} | \eta_{j\not{s_j}})$$

@@

$$\partial_{\phi_{js_ji}}\ln{\mathcal{L}}=1-P_i'(v_{js_j} | \eta_{js_j})$$

$$\partial_{\phi_{j\not{s_j}i}}\ln{\mathcal{L}}=-P_i'(v_{j\not{s_j}} | \eta_{j\not{s_j}})$$ 
\end{enumerate}
